### 2020-06-01 paper.tex
Fix Logical Mistake in Proposed Algorithm Section
Add Abstract Section

Vestibulum rhoncus est pellentesque elit ullamcorper dignissim cras tincidunt lobortis feugiat vivamus at augue eget arcu dictum varius duis at consectetur lorem donec massa sapien faucibus et molestie ac feugiat sed lectus vestibulum mattis ullamcorper velit sed ullamcorper morbi tincidunt ornare massa eget egestas purus viverra accumsan in nisl nisi scelerisque eu ultrices vitae auctor eu augue ut lectus arcu bibendum at varius vel pharetra vel turpis nunc eget lorem dolor sed viverra ipsum nunc aliquet bibendum enim facilisis gravida neque convallis a cras semper auctor neque vitae tempus quam pellentesque nec nam aliquam sem et tortor consequat id porta nibh venenatis cras sed felis eget velit aliquet sagittis id consectetur purus ut faucibus pulvinar elementum integer enim neque volutpat ac tincidunt vitae semper quis lectus nulla at volutpat diam ut venenatis tellus in metus vulputate eu scelerisque felis imperdiet proin fermentum leo vel orci porta non pulvinar neque laoreet

@@

\begin{algorithm}[H]
    \caption{Proposed Algorithm}
    \begin{algorithmic}[1]
    \renewcommand{\algorithmicrequire}{\textbf{Input:}}
    \renewcommand{\algorithmicensure}{\textbf{Output:}}
    \Require Circuit $C_{o}$
    \Ensure  Optimized placement configuration $\eta$
    \While{Population $\sigma$ is NOT filled completely}
        \State Generate an initial random cells placement $P$
        \State Set $\alpha = 0.995$
        \State Set temperature $T = 2 * number\; of\; cells\; of\; C_{o}$
        \State Set optimized circuit configuration $\Phi = P$
        \While{$T > 1$}
        \State $P^{'} = $ randomly generated cells placement
        \State $\Delta C = wirelength(P^{'}) - wirelength(P)$
        \If{$\Delta C < 0$}
            \State $P = P^{'}$
            \If{$wirelength(P) < wirelength(\Phi)$}
                \State $\Phi = P$
            \EndIf
        \ElsIf{$rand(0,1) < e^{-\Delta C/T}$}
            \State $P = P^{'}$
        \EndIf
        \State $T = T * \alpha$
        \EndWhile
        \State \textbf{Append} $\Phi$ to $\sigma$
    \EndWhile
    \While{The termination condition is NOT satisfied}
        \State Sort $\sigma$ in descending order by the fitness level
        \State $\sigma^{*} = crossover(\sigma)$
        \State $\sigma^{*} = mutation(\sigma^{*})$
        \algrenewcommand\algorithmicfor{\textbf{foreach}}
        \For{$\sigma^{*}_{i} \in \sigma^{*}$}
            \State Evaluate $\sigma^{*}_{i}$ fitness level
        \EndFor
        \State $\sigma = \sigma^{*}$
    \EndWhile
    \State $\eta = $ the fittest individual of $\sigma$
    \State \textbf{return} $\eta$
    \end{algorithmic} 
\end{algorithm}

>>>>

The simulated annealing algorithm is extensively used for cell placement in VLSI but its main downside is that it requires intensive computing to have optimum solutions in practical time. Genetic algorithms may get trapped in local minima, however, they traverse the solution space more rapidly. In this paper, simulated annealing and genetic algorithms are combined in order to achieve better solutions for VLSI cell placement. The genetic algorithm used is enhanced by taking the simulated annealing algorithm results as the initial population instead of generating random populations. Simulation outcome shows encouraging results in terms of overall wirelength.

@@

\begin{algorithm}[H]
    \caption{Proposed Algorithm}
    \begin{algorithmic}[1]
    \renewcommand{\algorithmicrequire}{\textbf{Input:}}
    \renewcommand{\algorithmicensure}{\textbf{Output:}}
    \Require Circuit $C_{o}$
    \Ensure  Optimized placement configuration $\eta$
    \State Generate an initial random cells placement $P$
    \While{Population $\sigma$ is NOT filled completely}
        \State Set $\alpha = 0.995$
        \State Set temperature $T = 2 * number\; of\; cells\; of\; C_{o}$
        \State Set optimized circuit configuration $\Phi = P$
        \While{$T > 1$}
        \State $P^{'} = $ randomly generated cells placement
        \State $\Delta C = wirelength(P^{'}) - wirelength(P)$
        \If{$\Delta C < 0$}
            \State $P = P^{'}$
            \If{$wirelength(P) < wirelength(\Phi)$}
                \State $\Phi = P$
            \EndIf
        \ElsIf{$rand(0,1) < e^{-\Delta C/T}$}
            \State $P = P^{'}$
        \EndIf
        \State $T = T * \alpha$
        \EndWhile
        \State \textbf{Append} $\Phi$ to $\sigma$
    \EndWhile
    \While{The termination condition is NOT satisfied}
        \State Sort $\sigma$ in descending order by the fitness level
        \State $\sigma^{*} = crossover(\sigma)$
        \State $\sigma^{*} = mutation(\sigma^{*})$
        \algrenewcommand\algorithmicfor{\textbf{foreach}}
        \For{$\sigma^{*}_{i} \in \sigma^{*}$}
            \State Evaluate $\sigma^{*}_{i}$ fitness level
        \EndFor
        \State $\sigma = \sigma^{*}$
    \EndWhile
    \State $\eta = $ the fittest individual of $\sigma$
    \State \textbf{return} $\eta$
    \end{algorithmic} 
\end{algorithm}
